---
title: ""
output: 
  html_document:
    code_ folding: hide
    includes:
      in_header: "favicon.html"
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# **AX task**

The AX task was conducted in Tamil Nadu via Gorilla. It was a between-subjects design with three groups: Clean, 15dB SNR, and 5dB SNR. We collected data from 64 participants: 20 in Clean, 24 in 15db SNR, and 20 in 5dB SNR. In hindsight we should have done it within-subjects, but I thought the experiment would take too long to complete. There were 120 items that tested discrimination of consonant contrasts in varying vowel environments. For example: ha-ka, ki-ti, pu-thu, etc.

## p-C discrimination

For the purposes of this task however, we're only interested in the p-C contrasts (this includes C-p as well).

Load the data:
```{r}
data_15 <- read.csv("Master_15_local.csv", header = TRUE)
data_5 <- read.csv("Master_5_local.csv", header = TRUE)
data_clean <- read.csv("Master_clean_local.csv", header = TRUE)
full_data <- rbind(data_clean,data_15,data_5)

# How many participants
num_unique_participants <- full_data %>%
  distinct(Participant.Private.ID) %>%
  nrow()
num_unique_participants

# Make new data frame with dental and retroflex symbols

#full_data_new <-  data.frame(
#  lapply(full_data, function(x) {
#    x <- gsub("th", "t̪", x)
#    x <- gsub("t", "ʈ", x)
#    return(x)
#  })
#)
```

Remove all the data except the p-C/C-p trials:
```{r}
# Full data clean
remove_rows <- function(full_data) {
  allowed_values <- c("p-th", "p-t", "p-k", "p-h")
  filtered_full_data <- subset(full_data, con %in% allowed_values)
  return(filtered_full_data)
}

filtered_full_data <- remove_rows(full_data)

# Make SNR a factor
filtered_full_data$snr <- as.factor(filtered_full_data$snr)
```

# Visualize the data

```{r}
## Make a master bar chart of proportion correct w error bars

library(ggplot2)
library(dplyr)

# new names for snr facet labels
snr_names <- list("clean"="SNR 15dB","15"="SNR 10dB", "5"="SNR 5 dB")

# use the labeller function in facet
snr_labeller <- function(variable,value){
  return(snr_names[value])
}

# Calculate the mean and standard error (SEM) for each group
summary_filtered_full_data <- filtered_full_data %>%
  group_by(snr, con) %>%
  summarise(mean_corr = mean(corr),
            sd_corr = sd(corr),
            n = n()) %>%
  mutate(se_corr = sd_corr / sqrt(n))  # Calculate Standard Error

# Order of SNRs in the plot
summary_filtered_full_data$snr_f = factor(summary_filtered_full_data$snr, levels=c('clean','15','5'))


# Plot using ggplot2
grey_colors <- c("grey20", "grey40", "grey60", "grey80")

AX_plot_grey <- ggplot(summary_filtered_full_data, aes(x = con, y = mean_corr, fill = con)) +
  geom_bar(stat = "identity", position = "dodge", show.legend = FALSE) + ylim(0,1)+
  geom_errorbar(aes(ymin = mean_corr - se_corr, ymax = mean_corr + se_corr),
                position = position_dodge(width = 0.9), width = 0.25) +
  facet_wrap(~snr_f,ncol = 3, labeller = snr_labeller) + 
  labs(x = "Contrast", y = "Proportion Correct", fill = "Contrast") +
  scale_x_discrete(labels=c("p-h", "p-k", "p-ʈ", "p-t̪")) +
  scale_fill_manual(values = grey_colors) + 
  theme_minimal()

AX_plot_color <- ggplot(summary_filtered_full_data, aes(x = con, y = mean_corr, fill = con)) +
  geom_bar(stat = "identity", position = "dodge", show.legend = FALSE) + ylim(0,1)+
  geom_errorbar(aes(ymin = mean_corr - se_corr, ymax = mean_corr + se_corr),
                position = position_dodge(width = 0.9), width = 0.25) +
  facet_wrap(~snr_f,ncol = 3, labeller = snr_labeller) + 
  labs(x = "Contrast", y = "Proportion Correct", fill = "Contrast") +
  scale_x_discrete(labels=c("p-h", "p-k", "p-ʈ", "p-t̪")) +
  theme_minimal()

#AX_plot_grey
AX_plot_color

ggsave('AX_plot_grey.png', bg="white", dpi=500, width = 4, height = 4)
ggsave('AX_plot_color.png', bg="white", dpi=500, width = 4, height = 4)

```

# **Model**

This is a very basic model with accuracy ("corr" in the data frame) as a function of group ("snr") crossed with contrast (4 levels:p-th, p-t, p-k,p-h). In the model the "clean" group (no added noise) is the reference for snr and "p-h" is the reference for contrast.

```{r}
library(lme4)
filtered_full_data$snr <- relevel(filtered_full_data$snr, ref = "clean")

model <- glmer(corr ~ snr * con + (1 | part), data = filtered_full_data, family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(model)
```

{r echo=FALSE}
library(texreg)
texreg(model, single.row = TRUE)
